FTLR proof cases

### 2018-06-24 fully-abstract-comp/ftlr-proof-cases.tex
explanation

        Assuming the above, we use our assumption that Theorem~\ref{thm:ftlr} holds for all $n' < n$ to get

>>>>

        Assuming the above, we use our assumption that Theorem~\ref{thm:ftlr} holds for all $n' < n$ (note that from assumption ``$\Phi_S$ reasonable up to $n$ steps'' and Lemma~\ref{lem:ec-reasonable-downwards-closed} and $n''' \le n'' < n - 1$ we get ``$\Phi_S$ reasonable up to $n'''+1$ steps'' from which it follows that ``$\Phi_S(\pcreg) + \calllen$ reasonable up to $n'''$ steps''.
        ) To get
